Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-22 ms/main.tex
revise fig 4 legend

\section*{Figures}
%%% Figure: model illustration
\begin{figure}[thb]
  \centering
  \includegraphics[scale=1]{figure1.pdf}
  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
  \label{fig:horizontal}
\end{figure}

@@

\begin{figure}[htb]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
    The vertical transmission rate $v$ is on the x-axis.
    Horizontal transmission bias (\textbf{a}) for cooperation, $T_A>T_B$ and (\textbf{b}) for defection, $T_A<T_B$.
    Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines in figures \textbf{(a)}, \textbf{(b)}. 
    Soical association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines in figures \textbf{(c)}, \textbf{(d)}.
    (\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.
    (\textbf{c}), $b=1.2$, $T_A=0.5$, $T_B = 0.4$, $c=0.5$.
    (\textbf{d}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $c=0.5$.}
    \label{fig:result3}
\end{figure}
\pagebreak

>>>>

\section*{Figures}
%%% Figure: model illustration
\begin{figure}[thb]
  \centering
  \includegraphics[scale=1]{figure1.pdf}
  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{social association} parameter.
  }
  \label{fig:horizontal}
\end{figure}

@@

\begin{figure}[htb]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
	In all cases the vertical transmission rate $v$ is on the x-axis.
	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines, respectively. 
    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively. 
    Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
    Here, $T_A = 0.5$, and
    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
    }
    \label{fig:result3}
\end{figure}
\pagebreak
